Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-06 Documents/Euler/Benchmarks1D/draft.tex
Reverting to article style

\documentclass[10pt,preprint]{aastex}

@@

\title{Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado}
\author{Juliana Pulsinelli\altaffilmark{1} and Eirik Endeve\altaffilmark{2}}

\altaffiltext{1}{Bearden High School, Knoxville, TN 37919-5449, USA}
\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T8.png} &
	  \includegraphics[width=.425\textwidth]{prs_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
  velocity (left panel) and pressure (right panel).}}
\end{figure}

>>>>

\documentclass[10pt]{article}

@@

\title{Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado}
%\author{Juliana Pulsinelli\altaffilmark{1} and Eirik Endeve\altaffilmark{2}}

%\altaffiltext{1}{Bearden High School, Knoxville, TN 37919-5449, USA}
%\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

\maketitle

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T8.png} &
	  \includegraphics[width=.425\textwidth]{prs_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
  velocity (left panel) and pressure (right panel).}
\end{figure}
